---
title: "Regression through the origin"
author: "Donghyung Lee"
date: "`r Sys.Date()`"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Regression through the origin.
**View the simple linear regression fit, and recall the discussion we had in class, adjust your model and fit a regression through the origin model (RTTO) instead. Obtain the estimated regression function.**
```{r}
data0120=read.table("http://www.stat.ufl.edu/~rrandles/sta4210/Rclassnotes/data/textdatasets/KutnerData/Chapter%20%201%20Data%20Sets/CH01PR20.txt")
colnames(data0120)=c("minutes","copiers_number")

fit2=lm(minutes~copiers_number-1,data=data0120)
summary(fit2)
```
The estimated regression function is $\hat{Y_i}=14.9472X_i$, (or estimated minutes=14.9472* copiers_number)

### Check the residuals.
**Check $\sum_{i=1}^{n}e_i\neq0$ and  $\sum_{i=1}^{n}e_iX_i=0$.**
```{r}
res=fit2$residuals
sum(res)
sum(data0120$copiers_number*res)
```
Based on the calculation above, $\sum_{i=1}^{n}e_i=-5.86$ is not equal to 0 and $\sum_{i=1}^{n}e_iX_i=-1.46*10^{-13}$, almost equal to 0.


### Confidence interval.
**Estimate $\beta_1$ with a 95\% confidence interval.**
```{r}
confint(fit2,,level=0.95)
```
The 95% confidence interval for $\beta_1$ is (14.49,15.40).

### Prediction interval.
**Predict the service time on a call in which six copiers are serviced. Use a 98\% confidence level.**
```{r}
predict(fit2,new=data.frame(copiers_number=6),interval="prediction",level=0.98,data=data0120)
```
The 98% prediction interval for the service time on a call in which 6 copiers are serviced is (68.15,111.22)

### Simultaneous prediction interval.
**Estimate the number of minutes spent when there are 2,3,4,5 copiers to be serviced. Use a 95\% family confidence coefficient and use Bonferroni method. **
```{r}
alphaF=1-0.95
g=4
alpha=alphaF/g
predict(fit2,new=data.frame(copiers_number=c(2,3,4,5)),interval = "pred",level=1-alpha,data=data0120)
```

The 95% simultaneous PI for the number of minutes spent when there're 2,3,4,5 copiers to be serviced is as above.
